---
title: "MS_Analysis_v4_20191128"
subtitle: "Classification of Impaired VS. Preserved Patient (n=183)"
author: "Dana Zeng"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  html_document:
    toc: true
    code_folding: hide
---
### Load the imputed dataset and subset for each model
* Model 1: Demographics ONLY (183*10)
* Model 2: Volumetric metrics ONLY (183*190)
* Model 3: Lesion (whole, no left & right )ONLY (T2) (183*43)
* Model 4: DTI ONLY (183*39)
* Model 5: Resting state ONLY (182*1514)
* Model 6: All top variables by RF


```{r setup, include=FALSE, warning=F}
knitr::opts_chunk$set(echo = TRUE, fig.width = 10, fig.height = 7)
library(tidyverse)
library(mice)
library(glmnet)
library(caret)
library(pROC)
library(randomForest)
library(broom)
library(knitr)
library(ggpubr)
library(Boruta)
library(ggthemes)
load("./MS_Datacreation_v2_imp.RData")
df <- df_imputed 
df_no128 <- df_imputed_no128 
rm(df_imputed, df_imputed_no128)
df_m1 <- df[,c(2:10,282)]
df_m2 <- df[,c(11:199,282)]
df_m3 <- df[,c(200:213,282)]
df_m4 <- df[,c(242:279,282)]
df_m5 <- df_no128[,c(283:1795,282)] 

iteration_control <- 101

cut_name <- function(x){
  for (i in 1:length(x)){
  if (nchar(x[i])<=50){
  x[i] = paste0(substr(x[i],1,str_locate_all(x[i],"_")[[1]][3,1]),
                "\n",
                substr(x[i],str_locate_all(x[i],"_")[[1]][3,1]+1,str_locate_all(x[i],"_")[[1]][6,1]),
                "\n",
                substr(x[i],str_locate_all(x[i],"_")[[1]][6,1]+1,nchar(x[i])))}
  else if (nchar(x[i])>50 ){
      x[i] = paste0(substr(x[i],1,str_locate_all(x[i],"_")[[1]][3,1]),
                "\n",
                substr(x[i],str_locate_all(x[i],"_")[[1]][3,1]+1,str_locate_all(x[i],"_")[[1]][6,1]),
                "\n",
                substr(x[i],str_locate_all(x[i],"_")[[1]][6,1]+1,str_locate_all(x[i],"_")[[1]][9,1]),
                "\n",
                substr(x[i],str_locate_all(x[i],"_")[[1]][9,1]+1,nchar(x[i])))}
  }  
  return(x)    
  }
```   


## Model 1 Demographics Only 
### Logistic Regression by each variable alone
```{r}
df_m1[,c(1,4:7,9)] <- scale(df_m1[,c(1,4:7,9)], scale = TRUE, center = TRUE)
df_m1$edss <- as.numeric(df_m1$edss)

nuemric <- tibble(
  var = names(df_m1)[c(1,4:9)],
  test = apply(df_m1[,c(1,4:9)], 2, function(x){
    return(tidy(glm(category~x, data = df_m1, family = "binomial")))
  })) 
categorical <- tibble(
  var = names(df_m1)[c(2,3)],
  test = apply(df_m1[,c(2,3)], 2, function(x){
    return(tidy(glm(category~x, data = df_m1, family = "binomial")))
  })) 
all <- rbind(nuemric, categorical) %>% unnest() %>% filter(term!="(Intercept)")
kable(all %>% mutate(var = ifelse(duplicated(var), "", as.character(var))))
```

## Fit Random Forest to Different Models
### Model 1: Demograhpic Variables
```{r}
auc_rf <- data_frame(iteration = NA, auc = NA,ci_low = NA,ci_high = NA)
roc_list_rf <- list()
mtry <-  data_frame(iteration=NA, mtry = NA)
df_m1$category <- factor(df_m1$category)
levels(df_m1$category) <- make.names(levels(df_m1$category))

set.seed(9999)
  for (i in 1:iteration_control){
      train_idx <- createDataPartition(df_m1$category, p = .8, list = FALSE, times = 1)
      train <- df_m1[train_idx,]
      test  <- df_m1[-train_idx,]

      result <- train(
        as.factor(category) ~ ., data = train,
        method = "rf",
        trControl = trainControl("cv", number = 5, savePredictions = TRUE, classProbs = TRUE),
        importance=T,
        ntree=500
      )
      ## Make Predictions
      pred <- predict(result, test, type = "prob")

      # Calculate ROC AND AUC
      roc <- roc(test$category, pred[,2], quiet = T)
      auc_result <- c(iteration = i, auc = ci(roc)[2], ci_low = ci(roc)[1], ci_high = ci(roc)[3])
      auc_rf <- rbind(auc_rf, auc_result)
      model_mtry <- c(iteration = i, mtry=result$bestTune[1,1])
      
      #Save mtry
      mtry <- rbind(mtry,model_mtry)

      # Save ROC Obeject for plot
      roc_list_rf[[i]] <- roc

  }
auc_rf <- auc_rf[-1,]
mtry <- mtry[-1,]

set.seed(9999)
boruta.train <- Boruta(as.factor(category) ~ ., data =df_m1,ntree=500,maxRuns= 2000)
print(boruta.train)
final.boruta <- TentativeRoughFix(boruta.train)


# Save plotting and table objects
auc_m1 <- mutate(auc_rf, model = "Demographic")
median_rf_m1 <- roc_list_rf[[which(auc_rf$auc==median(auc_rf$auc))[1]]]
boruta_m1 <- final.boruta
mtry_m1 <- mtry

```

### Model 2: Volumetric metrics ONLY (T1)
```{r, message="hide", result = "hide"}

auc_rf <- data_frame(iteration = NA, auc = NA,ci_low = NA,ci_high = NA)
var_imp_rf <- data.frame(variable = names(df_m2)[-190])
mtry <-  data_frame(iteration=NA, mtry = NA)
roc_list_rf <- list()

df_m2$category <- factor(df_m2$category)
levels(df_m2$category) <- make.names(levels(df_m2$category))

set.seed(9999)
  for (i in 1:iteration_control){
      train_idx <- createDataPartition(df_m2$category, p = .8, list = FALSE, times = 1)
      train <- df_m2[train_idx,]
      test  <- df_m2[-train_idx,]

      result <- train(
        as.factor(category) ~ ., data = train,
        method = "rf",
        trControl = trainControl("cv", number = 5, savePredictions = TRUE, classProbs = TRUE),
        importance=T,
        ntree=500
      )
      ## Make Predictions
      pred <- predict(result, test, type = "prob")

      # Calculate ROC AND AUC
      roc <- roc(test$category, pred[,2], quiet = T)
      auc_result <- c(iteration = i, auc = ci(roc)[2], ci_low = ci(roc)[1], ci_high = ci(roc)[3])
      auc_rf <- rbind(auc_rf, auc_result)
      model_mtry <- c(iteration = i, mtry=result$bestTune[1,1])
      
      #Save mtry
      mtry <- rbind(mtry,model_mtry)



      # Save ROC Obeject for plot
      roc_list_rf[[i]] <- roc

      # Save Var_important
      var_imp <- select(as_tibble (randomForest::importance(result$finalModel)),MeanDecreaseAccuracy)
      colnames(var_imp) <- paste0("iteration_",i)
      var_imp_rf <- cbind(var_imp_rf,var_imp)
  }
auc_rf <- auc_rf[-1,]
mtry <- mtry[-1,]

set.seed(9999)
boruta.train <- Boruta(as.factor(category) ~ ., data =df_m2,ntree=500,maxRuns= 2000)
print(boruta.train)
final.boruta <- TentativeRoughFix(boruta.train)


# Save plotting and table objects
auc_m2 <- mutate(auc_rf, model = "T1")
median_rf_m2 <- roc_list_rf[[which(auc_rf$auc==median(auc_rf$auc))[1]]]
boruta_m2 <- final.boruta
var_imp_m2 <- attStats(final.boruta) %>%
  tibble::rownames_to_column( "variable") %>%
  filter(decision == "Confirmed") %>%
  mutate(variable = fct_reorder(variable, meanImp))
mtry_m2 <- mtry

```

### Model 3: Lesion (whole, no left & right) ONLY (T2) (183*43)
```{r, message="hide", result = "hide"}

auc_rf <- data_frame(iteration = NA, auc = NA,ci_low = NA,ci_high = NA)
var_imp_rf <- data.frame(variable = names(df_m3)[-15])
mtry <-  data_frame(iteration=NA, mtry = NA)
roc_list_rf <- list()

df_m3$category <- factor(df_m3$category)
levels(df_m3$category) <- make.names(levels(df_m3$category))
set.seed(9999)

  for (i in 1:iteration_control){
      train_idx <- createDataPartition(df_m3$category, p = .8, list = FALSE, times = 1)
      train <- df_m3[train_idx,]
      test  <- df_m3[-train_idx,]

      result <- train(
        as.factor(category) ~ ., data = train,
        method = "rf",
        trControl = trainControl("cv", number = 5, savePredictions = TRUE, classProbs = TRUE),
        importance=T,
        ntree=500
      )
      ## Make Predictions
      pred <- predict(result, test, type = "prob")

      # Calculate ROC AND AUC
      roc <- roc(test$category, pred[,2], quiet = T)
      auc_result <- c(iteration = i, auc = ci(roc)[2], ci_low = ci(roc)[1], ci_high = ci(roc)[3])
      auc_rf <- rbind(auc_rf, auc_result)
      model_mtry <- c(iteration = i, mtry=result$bestTune[1,1])
      
      #Save mtry
      mtry <- rbind(mtry,model_mtry)



      # Save ROC Obeject for plot
      roc_list_rf[[i]] <- roc

      # Save Var_important
      var_imp <- select(as_tibble (randomForest::importance(result$finalModel)),MeanDecreaseAccuracy)
      colnames(var_imp) <- paste0("iteration_",i)
      var_imp_rf <- cbind(var_imp_rf,var_imp)
  }
auc_rf <- auc_rf[-1,]
mtry <- mtry[-1,]

set.seed(9999)
boruta.train <- Boruta(as.factor(category) ~ ., data = df_m3,ntree=500,maxRuns= 1500)
print(boruta.train)
final.boruta <- TentativeRoughFix(boruta.train)


# Save plotting and table objects
auc_m3 <- mutate(auc_rf, model = "T2")
median_rf_m3 <- roc_list_rf[[which(auc_rf$auc==median(auc_rf$auc))[1]]]
boruta_m3 <- final.boruta
var_imp_m3 <- attStats(final.boruta) %>%
  tibble::rownames_to_column( "variable") %>%
  filter(decision == "Confirmed") %>%
  mutate(variable = fct_reorder(variable, meanImp))
mtry_m3 <- mtry

```

### Model 4: DTI ONLY (183*39)
```{r, message="hide", result = "hide"}

auc_rf <- data_frame(iteration = NA, auc = NA,ci_low = NA,ci_high = NA)
var_imp_rf <- data.frame(variable = names(df_m4)[-39])
mtry <-  data_frame(iteration=NA, mtry = NA)
roc_list_rf <- list()

df_m4$category <- factor(df_m4$category)
levels(df_m4$category) <- make.names(levels(df_m4$category))

set.seed(9999)
  for (i in 1:iteration_control){
      train_idx <- createDataPartition(df_m4$category, p = .8, list = FALSE, times = 1)
      train <- df_m4[train_idx,]
      test  <- df_m4[-train_idx,]

      result <- train(
        as.factor(category) ~ ., data = train,
        method = "rf",
        trControl = trainControl("cv", number = 5, savePredictions = TRUE, classProbs = TRUE),
        importance=T,
        ntree=500
      )
      ## Make Predictions
      pred <- predict(result, test, type = "prob")

      # Calculate ROC AND AUC
      roc <- roc(test$category, pred[,2], quiet = T)
      auc_result <- c(iteration = i, auc = ci(roc)[2], ci_low = ci(roc)[1], ci_high = ci(roc)[3])
      auc_rf <- rbind(auc_rf, auc_result)
      model_mtry <- c(iteration = i, mtry=result$bestTune[1,1])
      
      #Save mtry
      mtry <- rbind(mtry,model_mtry)



      # Save ROC Obeject for plot
      roc_list_rf[[i]] <- roc

      # Save Var_important
      var_imp <- select(as_tibble (randomForest::importance(result$finalModel)),MeanDecreaseAccuracy)
      colnames(var_imp) <- paste0("iteration_",i)
      var_imp_rf <- cbind(var_imp_rf,var_imp)
  }
auc_rf <- auc_rf[-1,]
mtry <- mtry[-1,]

set.seed(9999)
boruta.train <- Boruta(as.factor(category) ~ ., data = df_m4,ntree=500,maxRuns= 1000)
print(boruta.train)
final.boruta <- TentativeRoughFix(boruta.train)


# Save plotting and table objects
auc_m4 <- mutate(auc_rf, model = "DTI")
median_rf_m4 <- roc_list_rf[[which(auc_rf$auc==median(auc_rf$auc))[1]]]
boruta_m4 <- final.boruta
var_imp_m4 <- attStats(final.boruta) %>%
  tibble::rownames_to_column( "variable") %>%
  filter(decision == "Confirmed") %>%
  mutate(variable = fct_reorder(variable, meanImp))
mtry_m4 <- mtry

```

###  Model 5: Resting State Only 182*1514
```{r, message="hide", result = "hide"}

auc_rf <- data_frame(iteration = NA, auc = NA,ci_low = NA,ci_high = NA)
var_imp_rf <- data.frame(variable = names(df_m5)[-1514])
mtry <-  data_frame(iteration=NA, mtry = NA)
roc_list_rf <- list()

df_m5$category <- factor(df_m5$category)
levels(df_m5$category) <- make.names(levels(df_m5$category))

set.seed(9999)
  for (i in 1:iteration_control){
      train_idx <- createDataPartition(df_m5$category, p = .8, list = FALSE, times = 1)
      train <- df_m5[train_idx,]
      test  <- df_m5[-train_idx,]

      result <- train(
        as.factor(category) ~ ., data = train,
        method = "rf",
        trControl = trainControl("cv", number = 5, savePredictions = TRUE, classProbs = TRUE),
        importance=T,
        ntree=500
      )
      ## Make Predictions
      pred <- predict(result, test, type = "prob")

      # Calculate ROC AND AUC
      roc <- roc(test$category, pred[,2], quiet = T)
      auc_result <- c(iteration = i, auc = ci(roc)[2], ci_low = ci(roc)[1], ci_high = ci(roc)[3])
      auc_rf <- rbind(auc_rf, auc_result)
      model_mtry <- c(iteration = i, mtry=result$bestTune[1,1])
      
      #Save mtry
      mtry <- rbind(mtry,model_mtry)


      # Save ROC Obeject for plot
      roc_list_rf[[i]] <- roc

      # Save Var_important
      var_imp <- select(as_tibble (randomForest::importance(result$finalModel)),MeanDecreaseAccuracy)
      colnames(var_imp) <- paste0("iteration_",i)
      var_imp_rf <- cbind(var_imp_rf,var_imp)
  }
auc_rf <- auc_rf[-1,]
mtry <- mtry[-1,]


set.seed(9999)
boruta.train <- Boruta(as.factor(category) ~ ., data = df_m5,ntree=500,maxRuns= 3000)
print(boruta.train)
final.boruta <- TentativeRoughFix(boruta.train)

# Save plotting and table objects
auc_m5 <- mutate(auc_rf, model = "RS")
median_rf_m5 <- roc_list_rf[[which(auc_rf$auc==median(auc_rf$auc))[1]]]
boruta_m5 <- final.boruta
var_imp_m5 <- attStats(final.boruta) %>%
  tibble::rownames_to_column( "variable") %>%
  filter(decision == "Confirmed") %>%
  mutate(variable = fct_reorder(variable, meanImp))
mtry_m5 <- mtry

```


### All Important Variables Model 183*60
```{r}
df_m6 <- df_no128 %>% select(pull(var_imp_m2,variable) %>% as.character(),
                    pull(var_imp_m3,variable) %>% as.character(),
                    pull(var_imp_m4,variable) %>% as.character(),
                    pull(var_imp_m5,variable) %>% as.character() ,
                    category)

auc_rf <- data_frame(iteration = NA, auc = NA,ci_low = NA,ci_high = NA)
var_imp_rf <- data.frame(variable = head(names(df_m6),-1))
mtry <-  data_frame(iteration=NA, mtry = NA)
roc_list_rf <- list()

df_m6$category <- factor(df_m6$category)
levels(df_m6$category) <- make.names(levels(df_m5$category))

set.seed(9999)
  for (i in 1:iteration_control){
      train_idx <- createDataPartition(df_m6$category, p = .8, list = FALSE, times = 1)
      train <- df_m6[train_idx,]
      test  <- df_m6[-train_idx,]

      result <- train(
        as.factor(category) ~ ., data = train,
        method = "rf",
        trControl = trainControl("cv", number = 5, savePredictions = TRUE, classProbs = TRUE),
        importance=T,
        ntree=500
      )
      ## Make Predictions
      pred <- predict(result, test, type = "prob")

      # Calculate ROC AND AUC
      roc <- roc(test$category, pred[,2], quiet = T)
      auc_result <- c(iteration = i, auc = ci(roc)[2], ci_low = ci(roc)[1], ci_high = ci(roc)[3])
      auc_rf <- rbind(auc_rf, auc_result)
      model_mtry <- c(iteration = i, mtry=result$bestTune[1,1])
      
      #Save mtry
      mtry <- rbind(mtry,model_mtry)



      # Save ROC Obeject for plot
      roc_list_rf[[i]] <- roc

      # Save Var_important
      var_imp <- select(as_tibble (randomForest::importance(result$finalModel)),MeanDecreaseAccuracy)
      colnames(var_imp) <- paste0("iteration_",i)
      var_imp_rf <- cbind(var_imp_rf,var_imp)
  }
auc_rf <- auc_rf[-1,]
mtry <- mtry[-1,]


set.seed(9999)
boruta.train <- Boruta(as.factor(category) ~ ., data = df_m6,ntree=500,maxRuns= 2500)
print(boruta.train)
final.boruta <- TentativeRoughFix(boruta.train)

# Save plotting and table objects
auc_m6 <- mutate(auc_rf, model = "All_Important")
median_rf_m6 <- roc_list_rf[[which(auc_rf$auc==median(auc_rf$auc))[1]]]
boruta_m6 <- final.boruta
var_imp_m6 <- attStats(final.boruta) %>%
  tibble::rownames_to_column( "variable") %>%
  filter(decision == "Confirmed") %>%
  mutate(variable = fct_reorder(variable, meanImp))

mtry_m6 <- mtry

```



## Results

### Plotting the Distribution of AUCs for all models
```{r}
rbind(auc_m1, auc_m2, auc_m3,auc_m4,auc_m5,auc_m6) %>%
  mutate(model = as.factor(model),
         model = fct_relevel(model, "Demographic","T1", "T2", "DTI", "RS","All_Important")) %>%
  ggplot(aes(x= model, y = auc, color = model))+
  geom_boxplot()+
  theme_bw()
```

### Plotting the EN VS. RF model with the median ROC
```{r}
par(pty = "s")
plot.roc(median_rf_m2, print.auc = T, col = 4 ,print.auc.y = .4)
plot.roc(median_rf_m3, print.auc = T, col = 3 ,print.auc.y = .35,add=T)
plot.roc(median_rf_m4, print.auc = T, col = 2 ,print.auc.y = .3,add=T)
plot.roc(median_rf_m5, print.auc = T, col = 1 ,print.auc.y = .25,add=T)
plot.roc(median_rf_m6, print.auc = T, col = 6 ,print.auc.y = .20,add=T)
legend("bottomright", legend = c("T1", "T2","DTI","RS","All_Important"), col = c(4,3,2,1,6), lwd = 4, cex=.5)

```


### Median ROC with CI
```{r}
auc_sum <- rbind(auc_m1,auc_m2, auc_m3,auc_m4,auc_m5,auc_m6)%>%
  select(auc,model) %>%
  group_by(model) %>%
  summarise(mean = mean(auc),
            sd = sd(auc),
            median = median(auc),
            ci_low = quantile(auc,0.025),
            ci_high  = quantile(auc,0.975)) %>%
  arrange(factor(model, levels = c("Demographic","T1", "T2", "DTI", "RS","All_Important")))
write.csv(auc_sum, "model_auc_summary_w_m1.csv")
kable(auc_sum)
```



### T1 Model

#### Important Variables
```{r}
confirm <- var_imp_m2 %>% pull(variable) %>% as.character()
top_var_m2 <- as_data_frame(boruta_m2$ImpHistory) %>%
  select(-c(shadowMax,shadowMean,shadowMin)) %>%
  select(confirm) %>%
  gather(everything(), key = variable, value = importance) %>%
  group_by(variable) %>%
  summarise(mean = mean(importance),
            sd = sd(importance),
            ci_low = quantile(importance,.025),
            ci_high = quantile(importance,.975)) %>%
  mutate(variable = fct_reorder(variable, mean)) %>%
  arrange(desc(mean))
#Plot top varss
  ggplot(top_var_m2,aes(x =variable, y=mean,fill = mean))+
  geom_bar(position="dodge",stat="identity")+
  geom_errorbar(aes(ymin = ci_low, ymax = ci_high), alpha=.7)+
  coord_flip()+
  ggtitle("T1 Model: Important Variables identified by Boruta")+
 theme_bw()
```

#### Top 5 Important Variables plot
```{r}
name <- top_var_m2 %>%
  arrange(desc(mean)) %>%
  head(5) %>%
  pull(variable) %>%
  as.character()
df_m2 %>%
  select(name,category) %>%
  mutate(category = recode(category, "X0" = "CP", "X1" = "CI")) %>%
  gather(1:5, key= variable, value = value) %>%
  mutate(variable = as.factor(variable),
         variable = fct_relevel(variable,name)) %>%
  group_by(variable,category) %>%
  mutate(median = median(value),
         sd=sd(value),
         ci_low = quantile(value,.025),
        ci_high = quantile(value,.975)) %>%
  ggplot(aes(x = category,y = value,color=category))+
  geom_jitter()+
  geom_errorbar(aes(ymin = ci_low, ymax = ci_high),color = "black")+
  facet_wrap(.~variable,scales = "free",nrow = 1)+
 theme_bw()
```



### T2 Model
#### Important Variables
```{r}
confirm <- var_imp_m3 %>% pull(variable) %>% as.character()
top_var_m3 <- as_data_frame(boruta_m3$ImpHistory) %>%
  select(-c(shadowMax,shadowMean,shadowMin)) %>%
  select(confirm) %>%
  gather(everything(), key = variable, value = importance) %>%
  group_by(variable) %>%
  summarise(mean = mean(importance),
            sd = sd(importance),
            ci_low = quantile(importance,.025),
            ci_high = quantile(importance,.975)) %>%
  mutate(variable = fct_reorder(variable, mean)) %>%
  arrange(desc(mean))
#Plot top vars
  ggplot(top_var_m3,aes(x =variable, y=mean,fill = mean))+
  geom_bar(position="dodge",stat="identity")+
  geom_errorbar(aes(ymin = ci_low, ymax = ci_high),alpha=.7)+
  coord_flip()+
  ggtitle("T2 Model: Important Variables identified by Boruta")+
 theme_bw()

```

#### Top 5 Important Variables plot
```{r}
name <- top_var_m3 %>%
  arrange(desc(mean)) %>%
  head(5) %>%
  pull(variable) %>%
  as.character()
df_m3 %>%
  select(name,category) %>%
  mutate(category = recode(category, "X0" = "CP", "X1" = "CI")) %>%
  gather(1:5, key= variable, value = value) %>%
  mutate(variable = as.factor(variable),
         variable = fct_relevel(variable,name)) %>%
  group_by(variable,category) %>%
  mutate(median = median(value),
         sd=sd(value),
         ci_low = quantile(value,.025),
        ci_high = quantile(value,.975)) %>%
  ggplot(aes(x = category,y = value,color=category))+
  geom_jitter()+
  geom_errorbar(aes(ymin = ci_low, ymax = ci_high),color = "black")+
  facet_wrap(.~variable,scales = "free",nrow = 1)+
 theme_bw()
```


### DTI Model
#### Important Variables
```{r}
confirm <- var_imp_m4 %>% pull(variable) %>% as.character()
top_var_m4 <- as_data_frame(boruta_m4$ImpHistory) %>%
  select(-c(shadowMax,shadowMean,shadowMin)) %>%
  select(confirm) %>%
  gather(everything(), key = variable, value = importance) %>%
  group_by(variable) %>%
  summarise(mean = mean(importance),
            sd = sd(importance),
            ci_low = quantile(importance,.025),
            ci_high = quantile(importance,.975)) %>%
  mutate(variable = fct_reorder(variable, mean)) %>%
  arrange(desc(mean))
#Plot top vars
  ggplot(top_var_m4,aes(x =variable, y=mean,fill = mean))+
  geom_bar(position="dodge",stat="identity")+
  geom_errorbar(aes(ymin = ci_low, ymax = ci_high), alpha=.7)+
  coord_flip()+
  ggtitle("DTI Model: Important Variables identified by Boruta")+
 theme_bw()
```

#### Top 5 Important Variables plot
```{r}
name <- top_var_m4 %>%
  arrange(desc(mean)) %>%
  head(5) %>%
  pull(variable) %>%
  as.character()

df_m4 %>%
  select(name,category) %>%
  mutate(category = recode(category, "X0" = "CP", "X1" = "CI")) %>%
  gather(1:5, key= variable, value = value) %>%
  mutate(variable = as.factor(variable),
         variable = fct_relevel(variable,name)) %>%
  group_by(variable,category) %>%
  mutate(median = median(value), sd=sd(value)) %>%
  ggplot(aes(x = category,y = value,color=category))+
  geom_jitter()+
  geom_errorbar(aes(ymin = median-sd, ymax = median+sd),color = "black")+
  facet_wrap(.~variable,scales = "free",nrow = 1)+
 theme_bw()
```


### RS Model
#### Important Variables
```{r}
confirm <- var_imp_m5 %>% pull(variable) %>% as.character()
top_var_m5 <- as_data_frame(boruta_m5$ImpHistory) %>%
  select(-c(shadowMax,shadowMean,shadowMin)) %>%
  select(confirm) %>%
  gather(everything(), key = variable, value = importance) %>%
  group_by(variable) %>%
  summarise(mean = mean(importance),
            sd = sd(importance),
            ci_low = quantile(importance,.025),
            ci_high = quantile(importance,.975)) %>%
  mutate(variable = fct_reorder(variable, mean)) %>%
  arrange(desc(mean))
#Plot top vars
  ggplot(top_var_m5,aes(x =variable, y=mean,fill = mean))+
  geom_bar(position="dodge",stat="identity")+
  geom_errorbar(aes(ymin = ci_low, ymax = ci_high), alpha=.7)+
  coord_flip()+
  ggtitle("RS Model: Important Variables identified by Boruta")+
 theme_bw()
```



#### Top 5 Important Variables plot
```{r}

##Plot top 5
name <- top_var_m5 %>%
  arrange(desc(mean)) %>%
  head(5) %>%
  pull(variable) %>%
  as.character()
df_m5 %>%
  select(name,category) %>%
  mutate(category = recode(category, "X0" = "CP", "X1" = "CI")) %>%
  gather(1:5, key= variable, value = value) %>%
  mutate(variable_n = cut_name(variable)) %>%
  mutate(variable = as.factor(variable),
         variable = fct_relevel(variable,name)) %>%
  group_by(variable,category) %>%
  mutate(median = median(value),
         sd=sd(value),
         ci_low = quantile(value,.025),
        ci_high = quantile(value,.975)) %>%
  ggplot(aes(x = category,y = value,color=category))+
  geom_jitter()+
  geom_errorbar(aes(ymin = ci_low, ymax = ci_high),color = "black")+
  facet_wrap(.~variable_n,scales = "free",nrow = 1,
             labeller =  label_wrap_gen(10,multi_line = TRUE))+
 theme_bw()
```

### All Important Variable Model
#### Important Variables
```{r}
confirm <- var_imp_m6 %>% pull(variable) %>% as.character()
top_var_m6 <- as_data_frame(boruta_m6$ImpHistory) %>%
  select(-c(shadowMax,shadowMean,shadowMin)) %>%
  select(confirm) %>%
  gather(everything(), key = variable, value = importance) %>%
  group_by(variable) %>%
  summarise(mean = mean(importance),
            sd = sd(importance),
            ci_low = quantile(importance,.025),
            ci_high = quantile(importance,.975)) %>%
  mutate(variable = fct_reorder(variable, mean)) %>%
  arrange(desc(mean))
#Plot top vars
  ggplot(top_var_m6,aes(x =variable, y=mean,fill = mean))+
  geom_bar(position="dodge",stat="identity")+
  geom_errorbar(aes(ymin = ci_low, ymax = ci_high), alpha=.7)+
  coord_flip()+
  ggtitle("All Important Variables Model: Important Variables identified by Boruta")+
 theme_bw()
```

#### Top 5 Important Variables plot
```{r}
cut_name_m6 <- function(x){
  for (i in 1:length(x)){
    if(nchar(x[i])<=20) {x[i] = x[i]}
    else if (nchar(x[i])>20){x[i] = cut_name(x[i])}
  }
  return(x)
}

name <- top_var_m6 %>%
  arrange(desc(mean)) %>%
  head(5) %>%
  pull(variable) %>%
  as.character()

top5_m6_df <- df_m6 %>%
  select(name,category) %>%
  mutate(category = recode(category, "X0" = "CP", "X1" = "CI")) %>%
  gather(1:5, key= variable, value = value)

name_cut <- cut_name_m6(name)

top5_m6_df %>%
  mutate(variable = cut_name_m6(variable),
        variable = as.factor(variable),
         variable = fct_relevel(variable,name_cut)) %>%
  group_by(variable,category) %>%
  mutate(median = median(value),
         sd=sd(value),
         ci_low = quantile(value,.025),
        ci_high = quantile(value,.975)) %>%
  ggplot(aes(x = category,y = value,color=category))+
  geom_jitter()+
  geom_errorbar(aes(ymin = ci_low, ymax = ci_high),color = "black")+
  facet_wrap(.~variable,scales = "free",nrow = 1)+
 theme_bw()
```

### Importance Output
```{r}
top_var_m2 <- top_var_m2 %>% mutate(method="T1")
top_var_m3 <- top_var_m3 %>% mutate(method="T2")
top_var_m4 <- top_var_m4 %>% mutate(method="DTI")
top_var_m5 <- top_var_m5 %>% mutate(method="RS")
top_var_m6 <- top_var_m6 %>% mutate(method="All_Important")
var_imp_all = rbind(top_var_m2,top_var_m3,top_var_m4,top_var_m5,top_var_m6) %>%
  select(method, everything()) %>%
  mutate(method = fct_relevel(method, "T1", "T2", "DTI", "RS","All_Important")) %>%
  arrange(method, desc(mean))
write.csv(var_imp_all,"important_var_importance.csv")
```

### t-test
```{r}
var_ttest <- filter(var_imp_all, method!="All_Important") %>% select(variable,method)
ttest <- df_no128%>% select(as.character(pull(var_ttest,variable)),category)
result <- lapply(ttest[,-length(ttest)],function(x){
  return(t.test(x,ttest$category)$p.value)
}) %>%
  unlist() %>%
  as.tibble() %>%
  mutate(variable = var_ttest$variable) %>%
  inner_join(var_ttest) %>%
  rename(p_value = value) %>%
  select(method, variable, p_value)
write.csv(result,"important_var_pvalue.csv")
```

### mtry output
```{r}
mtry_all <- rbind(mtry_m1,mtry_m2,mtry_m3,mtry_m4,mtry_m5,mtry_m6)
write.csv(mtry_all,"mtry_all.csv")
```
