---
title: "MS_Datacreation_v2_20191101"
author: "Dana Zeng"
date: "November 1, 2019"
output: 
  html_document:
    toc: true
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(mice)
library(table1)
library(readxl)
library(nnet)
library(knitr)
library(DT)
```

## Data Manipulation

### Load and Manipulate Data
 * releveled the category variable
 * filled the missing for depresison-sleep variable of healthy control with zero
```{r}
df <- readxl::read_xlsx ("./ML_all_11.05.xlsx", sheet = 1, col_names = TRUE, na = c("Nan","NaN"))
## Relevel the outcome and gender variable
df <- df %>% 
  janitor::clean_names() %>% 
  mutate(category = recode(x281, 
                                    `0` = "Cognitively Preserved" , 
                                    `1` = "Cognitively Impaired", 
                                     `2` = "Healthy Control"),
         sex = recode(sex, `1` = "Male", `2` = "Female")) %>% 
  mutate(edu_lev = as.factor(edu_lev),
         edss = as.factor(edss)) %>% 
  filter(category!="Healthy Control")


## Adding Zero to healthy control demographics
healthy <- which(is.na(df$depression)==T)
df$depression[healthy] <- rep(0,31)
df$anxiety[healthy] <- rep(0,31)
df$fatigue[healthy] <- rep(0,31)
df$edss[healthy] <- rep(0,31)
df$sleep[healthy] <- rep(0,31)

### create a new df filtering out 128 who has no correlation matrix
df_no128 <- df %>% filter(patient != 128)
```

### Resting State Screening
 * create another df without patient 128 who doesn't have correlation matrix
 * lower and diagonal filled with NA
 * The screening criteria is when both groups' coefficient is significant (1513 selected)
```{r,eval=F}
### Load MNI coordinate column names
change_sign <- function(x){
for (i in 1:length(x)){
  if (substr(x[i],1,1)=="-"){
    x[i] = str_replace (x[i], "-","N")
  }
  else if(substr(x[i],1,1)!="-") {
    x[i]=paste0("P",x[i])
  }}
  return(x)}
column_names <- read_excel("./Power_MNI_coordinates_names.xlsx") %>% 
  janitor::clean_names() %>%
  mutate_at(c("mni_coordiantes","x2","x3"),as.character) %>% 
  mutate_at(c("mni_coordiantes","x2","x3"),change_sign)
corr_col_names <- apply(column_names, 1, paste, collapse = ",")
corr_col_names <- gsub("'","",corr_col_names)
corr_col_names <- trimws(corr_col_names)


### Function for Corr for each Z matrix
corr_predictors <- function(path) {
  
corr <- read_delim(path, delim = " ", col_names = FALSE)
corr <- data.frame(corr)
colnames(corr) <- corr_col_names
rownames(corr) <- corr_col_names


corr[lower.tri(corr,diag=TRUE)]=NA
corr <- reshape2::melt(cbind(
  V1=rownames(corr), 
  as.data.frame(corr))
)
corr <- corr %>% drop_na(value)
colnames(corr) <- c("col", "row", "corr")
rownames(corr) <- NULL



corr <- corr %>% 
  mutate(MNI_Coordinates = paste0(col, "_", row)) %>% 
  select(MNI_Coordinates, corr)

MNI_Coordinates <- corr$MNI_Coordinates
rownames(corr) <- corr$MNI_Coordinates
corr <- corr %>% select(corr)
corr <- data.frame(t(corr))
colnames(corr) <- MNI_Coordinates

return(corr)
}

## Apply the function to 213 z matrices
files <- sapply(df_no128$patient, function(x) paste("./Z_matrices/", x, ".txt", sep = ""))
corr_mat <- do.call(rbind,lapply(files,corr_predictors))

# save(corr_mat,file="corr_mat_healthy.RData")
# load("./corr_mat_healthy.RData")

MS_Data<- corr_mat %>% 
  mutate(patient = df_no128$patient,
         category = df_no128$category) %>% 
  select(patient, everything()) %>% 
  remove_rownames() %>% 
    mutate(category = recode(category, "Cognitively Preserved" = 0, "Cognitively Impaired"  = 1))

rownames(MS_Data) <- NULL

vec <- data.frame(ind = NA, est =NA, pval = NA)
for (i in 2:34717){
sum_tb <- broom::tidy(glm(MS_Data[,34718] ~ (MS_Data)[,i], family = "binomial"))
vec_n <- unlist(c(ind = i, est = sum_tb[2,2], pval = sum_tb[2,5]))
vec <- rbind(vec,vec_n)
print(c(i, "done"))
}

vec_sig <- vec %>% filter(pval<0.05) %>% pull(ind)

rs_data <- MS_Data[,c(vec_sig,1,34718)]

# save(rs_data, vec_sig,MS_Data,file="rs_data.RData")
# load("./rs_data.RData")
```

### Merging Resting State Data with Demo+fMRI Data
* df_join (183*1795)
```{r,eval=F}
df <- df %>%  
  mutate(category = recode(category, "Cognitively Preserved" = 0, "Cognitively Impaired"  = 1))
df_no128 <- df_no128 %>% 
   mutate(category = recode(category, "Cognitively Preserved" = 0, "Cognitively Impaired"  = 1))
df_join <- left_join(df,rs_data) %>% janitor::clean_names()
df_join_no128 <- left_join(df_no128,rs_data) %>% janitor::clean_names()
# save(df_join, df_join_no128, file = "MS_Datacreation_v2_ori.Rdata")
```


### Missing Data Pattern
```{r}
na_count <- sapply(df, function(y) sum(length(which(is.na(y)))))
knitr::kable(na_count[na_count!=0], 
             col.names = "NA_counts",
             caption = "Variables that contain NAs")
no_na <- df %>% 
  select(-c(2:10)) %>% 
  drop_na() %>% pull(patient)

filter(df, patient %in% (no_na)==F) %>%
  select(patient,left_i_iv: right_x, mean_fa:rh_unc_md) %>% 
  knitr::kable(caption = "Patients (Other than Healthy Control) that contain NAs")
```

### Missing data imputation
 *  The missing data is imputated by using multiple imputation of cart with 10 iterations
 
```{r, message=F, eval=F}
# load("./MS_Datacreation_v2_ori.Rdata")
imp_result <- mice(df_join_no128[,c(172:279)],m=1,meth='cart',seed=500,remove.collinear = FALSE)
imp <- complete(imp_result)
df_imputed_no128 <- df_join_no128
df_imputed_no128[,c(172:279)] <- imp

## save the imputed df(both w/ or w/o 128)
df_imputed <- rbind(df_imputed_no128,df_join[127,])
# save(df_imputed,df_imputed_no128 ,file = "MS_Datacreation_v2_imp.Rdata")
```

#### load original/impuated datasets
```{r}
load("./MS_Datacreation_v2_ori.Rdata")
load("./MS_Datacreation_v2_imp.Rdata")
```


#### Missing data after imputation 
```{r}
df_imputed_no128 %>%
  filter(patient %in% c(3,29,95,114, 148, 152, 154, 169)) %>%
  select(patient, left_i_iv: right_x, mean_fa:rh_unc_md) %>%
  knitr::kable(caption = "Patients (Other than Healthy Control) that contain NAs after imputation")
```



## Descriptive statistics

### Demographics Descriptive Statistics
```{r}
df<- df_imputed %>% 
  mutate (category = recode(category,  `0` = "Cognitively Preserved" , `1` = "Cognitively Impaired"))
table1(~sex + age + edu_lev+ iq+ depression + anxiety + fatigue+ edss+ sleep| category, data=df, overall="Total")
```

### T1 Variables Descriptive Statistics
```{r}
t1_sum <- t(apply(df_imputed[,c(11:199)],2, summary))
datatable(t1_sum)
```

### T2 Variables Descriptive Statistics
```{r}
t2_sum <- t(apply(df_imputed[,c(200:241)],2, summary))
datatable(t2_sum)
```

### DTI Variables Descriptive Statistics
```{r}
t3_sum <- t(apply(df_imputed[,c(242:279)],2, summary))
datatable(t3_sum)
```


### RS Variables Descriptive Statistics
* Most of the minimum/maximum exceed the -1<RS<1 range, but not for the median.
```{r}
rs_sum <-  t(apply(df_imputed[,c(283:1795)],2, summary))
datatable(rs_sum)
```




